Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-06-22 prop_letter.tex
prop_letter.tex and "Kochen-Specker Theorem in QIVPM.pptx" Updating...

According to Mermin's comment\nb\citep{Mermin1999}, 
\begin{quote}
...although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case... 
\end{quote}
if the imperfection of the measurement is small enough, the finitely
precise measurement should not nullify the Kochen-Specker theorem.
This idea can be modeled precisely by considering the following kind
of QIVPMs.

@@

The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
QIVPM is to verify\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
 & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
\end{eqnarray}
\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$
which is a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).

When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
cannot be a subset of $\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$.
Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
The remain part of the proof are routine verification.\end{proof}

>>>>

According to Mermin's comment\nb\citep{Mermin1999}, 
\begin{quote}
...although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case... 
\end{quote}
if the imperfection of the measurement is small enough, the finitely
precise measurement should be close to idealized measurement, and
cannot nullify the Kochen-Specker theorem. This idea can be modeled
precisely by considering the following kind of QIVPMs.

@@

The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
QIVPM is to verify a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
 & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
\end{eqnarray}
\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$.

When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$
which implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
cannot be a subset of $\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$.
Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.

The remain part of the proof are routine verification.\end{proof}
